A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-03-16 index.Rmd
Reknit with new theme
Add acknowledgments

For completeness We also evaluated the efficacy of spray schedules on disease severity in the field.

@@

>>>>

For completeness, we also evaluated the efficacy of spray schedules on disease severity in the field.

@@

## Acknowledgments  
This meta-analysis was carried out with the funding assistance of the Grains Research and Development Corporation in Australia. Raw data for this work were contributed by the University of Southern Queensland, Queensland Department of Agriculture, Fisheries and Forestry (DAF), the Northern Grower Alliance. Additional thanks to Malcolm Riley, Sue Thompson and Lawrie Price.
